\textit{Rubrics Criteria:}
\begin{itemize}
    \item \textbf{Organization and Structure} (out of 5 marks)
    \begin{enumerate}
        \item Have the group members filled out the rubrics in the report?
            \answerTODO{}
        \item Does the submission provide a runnable implementation of \texttt{NIDS.py}?
            \answerTODO{}
        \item Does the write-up mention all required sections: \texttt{Abstract}, \texttt{Task Definition}, \texttt{Infrastructure}, \texttt{Approach}, \texttt{Literature Review}, \texttt{Experiments and Analysis}, \texttt{Contributions}, \texttt{References}?
            \answerTODO{}
        \item Does the write-up adhere to the maximum one page limit for the feature selection results and analysis requirement?
            \answerTODO{}
        \item Does the write-up adhere to the maximum eight page limit for the report requirement?
            \answerTODO{}
    \end{enumerate}
    \item \textbf{Content} (out of 48 marks)
    \begin{itemize}
        \item \texttt{Abstract} (out of 3 marks)
        \begin{enumerate}
            \item Does the abstract contain 200 words or less?
                \answerTODO{}
            \item Does it explain what is the write-up about?
                \answerTODO{}
            \item Does it explain the key findings of the project?
                \answerTODO{}
        \end{enumerate}
        \item \texttt{Task Definition} (out of 3 marks)
        \begin{enumerate}
            \item Does it provide the problem statement?
                \answerTODO{}
            \item Does it provide the evaluation metrics?
                \answerTODO{}
            \item Does it refrain from putting anything related to the solution, implemented source code, results and analysis?
                \answerTODO{}
        \end{enumerate}
        \item \texttt{Infrastructure} (out of 2 marks) 
        \begin{enumerate}
            \item Does it properly discuss the infrastructure used and required for running the code?
            \answerTODO{}
            \item Does it provide information and guidelines on how to run the code in both train and inference modes?
            \answerTODO{}
        \end{enumerate}
        \item \texttt{Approach} (out of 9 marks)
        \begin{enumerate}
            \item Does it explain how the data is split as well as the sizes of each split?
                \answerTODO{}
            \item Does it mention the different selected feature selection techniques (one for each member), how each technique works and how it can help in feature selection (out of 4 marks)?
                \answerTODO{}
            \item Does it mention the different classification techniques used in parts 2 and 3 (at least on per group member), and explain how each classifier works (out of 4 marks)?
                \answerTODO{}
        \end{enumerate}
        \item \texttt{Literature Review} (out of 2 marks) 
        \begin{enumerate}
            \item Does it discuss other places and possibly publications that have tried tackling this task (out of 2 marks)?
                \answerTODO{}
        \end{enumerate}
        \item \texttt{Experiments and Analysis} (out of 26 marks)
        \begin{enumerate}
            \item Does it provide the different feature selection experiments (one for each member), and explain which one is selected and why (out of 4 marks)?
                \answerTODO{}
            \item Does it provide the classification experiment with and without feature selection on both Label and attack cat (out of 2 marks)?
                \answerTODO{}
            \item Does it explain the process of finding the best settings for each selected different classifier as well as the classification scores for Label on the held-out split test set (out of 6 marks)?
                \answerTODO{}
            \item Does it explain which classifier worked the best for Label and explain why it worked better than the others?
                \answerTODO{}
            \item Do the Label classifier results show F1 scores above 0.9? 
                \answerTODO{}
            \item Do the Label classifier results get F1 scores above 0.85 on my held-out test-set?
                \answerNA{You don't have access to this test set}.
            \item Does it explain the process of finding the best settings for each selected different classifier as well as the Micro-F1 and Macro-F1 classification scores for attack\_cat on the held-out split test set (out of 6 marks)?
                \answerTODO{}
            \item Does it explain which classifier worked the best for attack\_cat and explain why it worked better than the others?
                \answerTODO{}
            \item Does it explain what is the main issue in the dataset that the attack\_cat classifiers would suffer from and what was the approach to deal with it?
                \answerTODO{}
            \item Do the attack\_cat classifier results show Macro-F1 scores above 0.45?
                \answerTODO{}
            \item Do the attack\_cat classifier results get Macro-F1 scores above 0.40 and Micro-F1 scores above 0.85 on my held-out test-set?
                \answerNA{You don't have access to this test set}.
            \item Do the classification experiments (on both Label and attack\_cat) handle the train and inference modes separately in a correct format (by possibly sending in model files or receiving the train dataset name as well as the held-out set if training is fast)?
                \answerTODO{}
        \end{enumerate}
        \item \texttt{Contributions} (out of 1 mark)
        \begin{enumerate}
            \item Does it provide enough explanations on the contributions of each member as well as the contribution percentage?
                \answerTODO{}
        \end{enumerate}
        \item \texttt{References} (out of 2 marks)
        \begin{enumerate}
            \item Is each bibliography item cited at least once in the write-up?
                \answerTODO{}
            \item Is bibliography/citation format consistent across the write-up and the write-up follows a standard bibliography style?
                \answerTODO{}
        \end{enumerate}
    \end{itemize}
    \item \textbf{Readability} (out of 5 marks)
    \begin{enumerate}
        \item Does the write-up have any spelling errors?
            \answerTODO{}
        \item Does the write-up have any grammar errors?
            \answerTODO{}
        \item Does the write-up have a proper and logical flow of information (grade out of 3)?
            \answerTODO{}
    \end{enumerate}
    \item \textbf{Total Grade}: out of the 58 marks, what would be a fair grade for your submission from your point of view?
        \answerTODO{}
\end{itemize}
